# Data Exploration

```{r loading data exploring, include = FALSE}
source("get_data.r")
source("clean_data.r")
source("prepare_data.r")
source("define_models.r")
```

## List of independent and dependent variables
Dependent variables only reported for the left side of body

```{r}
knitr::kable(df_vars_indep, caption = "List of independent variables")
knitr::kable(df_vars_dep, caption = "List of dependent variables")
```

## Exploring demographics
The number of females are a little bit higher than males. Age distribution does not match the age distribution of USA population. Therefore, estimations based on this sample may predict outcome variables for young people better than old ones.

```{r demographics, fig.height=3, fig.width=6}
vars = c("RIAGENDR", "RIDAGEEX")
df <- df_join[vars]
knitr::kable(describe(df), digits = 3, caption = "Summary of demographic variables")

ggplot(data = df, aes(x = RIDAGEEX)) + 
  geom_histogram() + 
  xlab("Age (Month)") +
  ylab("Count") + 
  ggtitle("Histogram of age")
```

## Exploring body measurements
Some of the variables show strong linear correlations and should be avoided as independent variables in regression analysis.

```{r body measurements, fig.height=9, fig.width=12}
vars <- c("BMXWT", "BMXHT", "BMXARMC", "BMXARML", "BMXCALF", "BMXLEG", 
          "BMXSUB", "BMXTHICR", "BMXTRI", "BMXWAIST")
df <- df_join[vars]
knitr::kable(describe(df), digits = 3, caption = "Summary of body measurement variables")

vec_row_sample <- sample(seq_len(nrow(df)), size = 1000)
ggpairs(df[vec_row_sample, ], colour = "cyl",
    upper = list(continuous = wrap("cor", size = 3)),
    lower = list(continuous = wrap("points", alpha = 0.3, size=0.2)),
    Progress = FALSE)
```

## Exploring DXA - Body parts fat weight
Data was only ploted for the left arm and leg

```{r dxa body fat}, fig.height=5, fig.width=7}
vars <- c("DXXHEFAT", "DXXLAFAT", "DXXLLFAT", "DXXTRFAT", "DXDTOFAT")
df <- df_join[vars]
knitr::kable(describe(df), digits = 3, caption = "Summary of body parts fat weights")

vec_row_sample <- sample(seq_len(nrow(df)), size = 1000)
ggpairs(df[vec_row_sample, ], colour = "cyl",
    upper = list(continuous = wrap("cor", size = 3)),
    lower = list(continuous = wrap("points", alpha = 0.3, size=0.2)),
    Progress = FALSE)
```

## Exploring DXA - Body parts total weight
Data was only ploted for the left arm and leg

```{r dxa body weight}, fig.height=4, fig.width=6}
vars <- c("DXDHETOT", "DXDLATOT", "DXDLLTOT", "DXDTRTOT")
df <- df_join[vars]
knitr::kable(describe(df), digits = 3, caption = "Summary of body parts total weights")

vec_row_sample <- sample(seq_len(nrow(df)), size = 1000)
ggpairs(df[vec_row_sample, ], colour = "cyl",
    upper = list(continuous = wrap("cor", size = 3)),
    lower = list(continuous = wrap("points", alpha = 0.3, size=0.2)),
    Progress = FALSE)
```
