# loading raw data
``` {r}
setwd("./")
source("get_data.r")
source("clean_data.r")
source("prepare_data.r")

print(data.frame(vars_indep, vars_indep_desc))
print(data.frame(vars_dep, vars_dep_desc))
```

# exploring demographic dataframe
The number of females are a little bit higher than males.
Age distribution does not match the age distribution of USA population. Therefore, estimations based on this sample may predict outcome variables for young people better than old ones.
``` {r}
vars = c("RIAGENDR", "RIDAGEEX")
df <- df_join[vars]

summary(df)

ggplot(data = df, aes(x = RIDAGEEX)) + geom_histogram() + xlab("Age (Month)") +
  ylab("Count") + ggtitle("Histogram of age")
```

# exploring body measurements dataframe
Some of the variables show strong linear correlations and should be avoided as independent variables in regression analysis.
``` {r}
vars <- c("BMXWT", "BMXHT", "BMXARMC", "BMXARML",
    "BMXCALF", "BMXLEG", "BMXSUB", "BMXTHICR", "BMXTRI", "BMXWAIST")
df <- df_join[vars]
summary(df)

vec_row_sample <- sample(seq_len(nrow(df)), size = 200)
ggpairs(df[vec_row_sample, ])
```

# exploring DXA dataframe
``` {r}
vars <- c("DXXHEFAT", "DXDHETOT", "DXXLAFAT", "DXDLATOT", "DXDLLTOT", "DXXLLFAT",
          "DXXRAFAT", "DXDRATOT", "DXXRLFAT", "DXDRLTOT", "DXXTRFAT", "DXDTRTOT", 
          "DXDTOBMC", "DXDTOBMD", "DXDTOFAT")
df <- df_join[vars]
summary(df)

vec_row_sample <- sample(seq_len(nrow(df)), size = 200)
ggpairs(df[vec_row_sample, ])
```